Target Markdown

### 2024-04-24 _targets.Rmd
Update manuscript results, discussion and methods

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      filter(!str_detect(Response, "~~")) %>% #Remove correlation w_avg_tlvl ~~ avg_omnivory
      mutate(across(c("Response", "Predictor"), ~var_replacement()[.x])) %>%
      mutate(Std.Estimate = round(Std.Estimate, 2)) %>%
      rename(`Std estimate` = Std.Estimate) %>%
      select(-Signif)
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF)
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(tab_sem_simplified_eff,
    sem_simplified_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  )
)
```

@@

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff)),
  tar_target(sem_main_text_file, here::here("data", paste0("sem_main_text_", names)), format = "file"),
  tar_target(sem_main_text, { readRDS(sem_main_text_file) }),
  tar_target(sem_main_text_eff_file, here::here("data", paste0("sem_main_text_eff_", names)), format = "file"),
  tar_target(sem_main_text_eff, { readRDS(sem_main_text_eff_file) }),
  tar_target(sem_main_text_collinearity_file, here::here("data", paste0("sem_main_text_collinearity_", names)), format = "file"),
  tar_target(sem_main_text_collinearity, { readRDS(sem_main_text_collinearity_file) }),
  tar_target(sem_main_text_rsquared_file, here::here("data", paste0("sem_main_text_rsquared_", names)), format = "file"),
  tar_target(sem_main_text_rsquared, { readRDS(sem_main_text_rsquared_file) }),
  tar_target(sem_main_text_coeff_file, here::here("data", paste0("sem_main_text_coeff_", names)), format = "file"),
  tar_target(sem_main_text_coeff, { readRDS(sem_main_text_coeff_file) }),
  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff))
)
```

```{targets group-all-analysis}
list(
  tar_target(sem_main_text_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "kno"),
      eff = list(
        sem_main_text_eff_tab_csc_rerun,
        sem_main_text_eff_tab_csc_non_allo,
        sem_main_text_eff_tab_csc_rebuild,
        sem_main_text_eff_tab_csc_kno
        ),
      collinearity = list(
        sem_main_text_collinearity_csc_rerun,
        sem_main_text_collinearity_csc_non_allo,
        sem_main_text_collinearity_csc_rebuild,
        sem_main_text_collinearity_csc_kno
        ),
    )
  ),
  tar_target(sem_main_text_eff_tab_tot,
    sem_main_text_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_main_text_eff_tab_tot,
    sem_main_text_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_csc_rerun),
  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun)
)
```

```{targets model-to-pred}
list(
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(default_variable_values_pred,
    c(
      "resp_div" = mean(sim_fw$resp_div),
      "env_stoch" = mean(sim_fw$env_stoch),
      "ct_alive" = mean(sim_fw$ct_alive),
      "avg_int_strength" = mean(sim_fw$avg_int_strength),
      "c" = mean(sim_fw$c),
      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
      "Z" = mean(sim_fw$Z)
    )
  ),
  tar_target(pred_range_fw,
    map(rlang::set_names(c("avg_int_strength", "ct_alive", "w_avg_tlvl")),
      ~quantile(sim_fw[[.x]], probs = c(.05, .95))
    )
  ),
  tar_target(pred_stab_comp_resp_div,
    fixed_effect_fw_stab_comp %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(
                min(pred_range_fw$avg_int_strength),
                max(pred_range_fw$avg_int_strength),
                length.out = 50
                ),
              seq(
                min(pred_range_fw$w_avg_tlvl),
                max(pred_range_fw$w_avg_tlvl),
                length.out = 50
              ),
              seq(
                min(pred_range_fw$ct_alive),
                max(pred_range_fw$ct_alive),
                length.out = 50
              )
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)

@@

@@

```{r, eval = FALSE}
tar_load(sem_main_text_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
tar_read(sem_main_text_eff_rerun)
tar_load(pred_stab_comp_resp_div)
```

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_main_text_eff_tab_csc_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      p_sem_tot_stab +
        theme(
          legend.position = "none",
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_main_text.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      p_sem_tot_stab +
        guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto"
  )
  ),
  tar_target(p_sem_fig_file,
    ggsave_multiple(
      paste0("p_sem_fig", c(".png", ".pdf")),
      plot = p_sem_fig,
      path = here::here("report", "figures"),
      scale = 3.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm")
  ),
  tar_target(p_sem_tot_stab_file,
    ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

>>>>

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF)
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(tab_sem_simplified_eff,
    sem_simplified_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  ),
  tar_target(tab_sem_doak_eff,
    sem_doak_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  )
)
```

@@

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff)),
  tar_target(sem_main_text_file, here::here("data", paste0("sem_main_text_", names)), format = "file"),
  tar_target(sem_main_text, { readRDS(sem_main_text_file) }),
  tar_target(sem_main_text_eff_file, here::here("data", paste0("sem_main_text_eff_", names)), format = "file"),
  tar_target(sem_main_text_eff, { readRDS(sem_main_text_eff_file) }),
  tar_target(sem_main_text_collinearity_file, here::here("data", paste0("sem_main_text_collinearity_", names)), format = "file"),
  tar_target(sem_main_text_collinearity, { readRDS(sem_main_text_collinearity_file) }),
  tar_target(sem_main_text_rsquared_file, here::here("data", paste0("sem_main_text_rsquared_", names)), format = "file"),
  tar_target(sem_main_text_rsquared, { readRDS(sem_main_text_rsquared_file) }),
  tar_target(sem_main_text_coeff_file, here::here("data", paste0("sem_main_text_coeff_", names)), format = "file"),
  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff)),

  tar_target(sem_doak_file, here::here("data", paste0("sem_doak_", names)), format = "file"),
  tar_target(sem_doak, { readRDS(sem_doak_file) }),
  tar_target(sem_doak_eff_file, here::here("data", paste0("sem_doak_eff_", names)), format = "file"),
  tar_target(sem_doak_eff, { readRDS(sem_doak_eff_file) }),
  tar_target(sem_doak_eff_tab, from_semEff_to_table(sem_doak_eff)),
  tar_target(sem_doak_collinearity_file, here::here("data", paste0("sem_doak_collinearity_", names)), format = "file"),
  tar_target(sem_doak_collinearity, { readRDS(sem_doak_collinearity_file) }),
  tar_target(sem_doak_rsquared_file, here::here("data", paste0("sem_doak_rsquared_", names)), format = "file"),
  tar_target(sem_doak_rsquared, { readRDS(sem_doak_rsquared_file) })
)
```

```{targets group-all-analysis}
  tar_target(sem_main_text_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "kno"),
      eff = list(
        sem_main_text_eff_tab_csc_rerun,
        sem_main_text_eff_tab_csc_non_allo,
        sem_main_text_eff_tab_csc_rebuild,
        sem_main_text_eff_tab_csc_kno
      collinearity = list(
        sem_main_text_collinearity_csc_rerun,
        sem_main_text_collinearity_csc_non_allo,
        sem_main_text_collinearity_csc_rebuild,
        sem_main_text_collinearity_csc_kno
  tar_target(sem_doak_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "kno"),
      eff = list(
        sem_doak_eff_tab_csc_rerun,
        sem_doak_eff_tab_csc_non_allo,
        sem_doak_eff_tab_csc_rebuild,
        sem_doak_eff_tab_csc_kno
      collinearity = list(
        sem_doak_collinearity_csc_rerun,
        sem_doak_collinearity_csc_non_allo,
        sem_doak_collinearity_csc_rebuild,
        sem_doak_collinearity_csc_kno
  tar_target(sem_main_text_eff_tab_tot,
    sem_main_text_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_main_text_eff_tab_tot,
    sem_main_text_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
  tar_target(sem_doak_eff_tab_tot,
    sem_doak_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_doak_eff_tab_tot,
    sem_doak_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")

```{targets simplified-sem}
list(
  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_csc_rerun),
  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_doak_eff_tab, sem_doak_eff_tab_csc_rerun)
)
```

```{targets model-to-pred}
list(
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(default_variable_values_pred,
    c(
      "resp_div" = mean(sim_fw$resp_div),
      "env_stoch" = mean(sim_fw$env_stoch),
      "ct_alive" = mean(sim_fw$ct_alive),
      "avg_int_strength" = mean(sim_fw$avg_int_strength),
      "c" = mean(sim_fw$c),
      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
      "Z" = mean(sim_fw$Z)
    )
  ),
  tar_target(pred_range_fw,
    map(rlang::set_names(c("avg_int_strength", "ct_alive", "w_avg_tlvl")),
      ~quantile(sim_fw[[.x]], probs = c(.05, .95))
    )
  ),
  tar_target(pred_stab_comp_resp_div,
    fixed_effect_fw_stab_comp %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(
                min(pred_range_fw$avg_int_strength),
                max(pred_range_fw$avg_int_strength),
                length.out = 50
                ),
              seq(
                min(pred_range_fw$w_avg_tlvl),
                max(pred_range_fw$w_avg_tlvl),
                length.out = 50
              ),
              seq(
                min(pred_range_fw$ct_alive),
                max(pred_range_fw$ct_alive),
                length.out = 50
              )
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)

@@

```{targets full-model-pred}
list(
  tar_target(model_fw_stab_comp_full,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_full_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_full_scaled_coeff,
    model_fw_stab_comp_full_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp_full,
    model_fw_stab_comp_full %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(pred_stab_comp_full_resp_div,
    fixed_effect_fw_stab_comp_full %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp_full$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(
                min(pred_range_fw$avg_int_strength),
                max(pred_range_fw$avg_int_strength),
                length.out = 50
                ),
              seq(
                min(pred_range_fw$w_avg_tlvl),
                max(pred_range_fw$w_avg_tlvl),
                length.out = 50
              ),
              seq(
                min(pred_range_fw$ct_alive),
                max(pred_range_fw$ct_alive),
                length.out = 50
              )
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = default_variable_values_pred
          )
        }
        )
    ) %>%
    select(-fix_effect, -values) %>%
    select(-variable) %>%
    mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(resp_div, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)
  ),
  tar_target(p_pred_stab_comp_full_resp_div,
    pred_stab_comp_full_resp_div %>%
  filter(response == "stab_com") %>%
  mutate(
    variable = var_replacement()[variable]
    ) %>%
  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y", strip.position = "left") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = resp_div_cat_colors()["Low"],
    mid = "white",
    high = resp_div_cat_colors()["High"],
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = var_replacement()["resp_div"],
    y = "Food-web structure",
    fill = "Slope community stability - Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, t = 5, unit = "pt"),
    strip.placement = "outside",
    strip.background = element_blank(),
    strip.text = element_text(size = 11),
    axis.title.y = element_blank()
  )
    )
)
```

@@

```{r, eval = FALSE}
tar_load(sem_main_text_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
tar_read(sem_main_text_eff_rerun)
tar_load(pred_stab_comp_resp_div)
library(targets)
tar_load(sem_doak_eff_tab_csc_rerun)
sem_doak_eff_tab_csc_rerun %>%
  filter(effect_type == "direct", abs(effect) > .05) %>%
  print(n = 40)

sem_doak_eff_tab_csc_rerun %>%
  filter(effect_type == "direct") %>%
  print(n = 40)
```
